\textbf{\sc Towards Deliberative Control in Marine Robotics}

### 2012-02-24 trunk/future.tex
added paragraph about europa's capabilities that could benefit t-rex in the future.

More specifically to \eu level we would like to improve \rx
integration of \eu ability to deliberate about resources. More
specifically we need to ba able to update resource level as 
modeled by \eu based on \rx observation.  As of today the 
support of resource is limited inside the \eu solver and there's no
direct way for \rx to update them dynamically based on recent
observations. This result on a potential discrepeancy between measured
given by, for example, the battery as modeled in \eu and the current
battery level as read in a \rx timeline. Finding an automated way to
link these two constructs would allow the plan to dynamically readapt
when these two values differs -- for example if the vehicle looses a
battery bank during a mission.

>>>>

At the \eu level we would like to improve \rx
integration of \eu ability to deliberate about resources. More
specifically we need to be able to update resource level as 
modeled by \eu based on \rx observation.  
Keeping the link between these two constructs automatically updated 
would allow the plan to dynamically adapt when these two values differ -- 
for example if the vehicle looses a battery bank during a mission.
Work is being done on \eu to provide enhanced modeling
capabilities and more powerful domain-independent search, these
would make it easier for \rx users to create domain models and to 
perform more ambitious deliberation.
